### 2018-05-19 msc_diploma_cubesat_galgoczi.tex
aa
update

High energy astrophysics

The main aim of the paper, therefore this thesis is to optimize the scintillators of the CubeSats (miniaturized satellites) in the Constellation Gamma satellites. It is not known which would be the best detector configuration for the detection of GRBs. In the

 The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.

@@

Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} have been studied already about four decades, nonetheless their origin is still not fully understood. They are one of the most extreme explosive events ever observed. In spite of tremendous effort and numerous observations there are still open questions concerning their detailed physics. GRBs were discovered in years 1967–73 by military Vela satellites and later reported to the scientific community in early seventies \cite{grb5}. They occur roughly once per day and are characterized by flashes of $\gamma$-rays typically lasting from a fraction of a second to thousands of seconds, typically in the energy range from several keV to several MeV, however $\gamma$-rays of energy >1 GeV associated with GRBs were detected as well. A GRB event outshines any other gamma-ray source on the sky.
It has been found that the duration distribution of their $\gamma$-ray prompt emission is bimodial \cite{grb6} which suggested that there were two groups of GRBs. Later, based on more observations, it has been confirmed that these two GRB groups were two distinct astrophysical populations \cite{grb6,grb7,grb8}: I. so called long GRBs (LGRBs) with softer spectrum and with prompt $\gamma$-ray emission $\geqslant$2 s that were identified to be gravitational collapses of massive stars due to their association with type Ic core-collapse supernovae, and II. so called short GRBs (SGRBs) with harder spectrum and with prompt $\gamma$-ray emission $\leqslant$2 s originating in merger of two compact objects such as neutron star - neutron star (NS-NS) or neutron star - black hole (NS-BH) \cite{grb9}.

@@

It was proposed that GRBs were created in collisions of highly relativistic outflow of the accelerated jetted matter \cite{grb10}. In many cases it was found that the prompt $\gamma$-ray emission is followed by longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11} explained as a result of the propagation of a relativistic shockwave through the circumburst medium. The suggestion that GRBs lie at cosmological distances \cite{grb12} was confirmed by numerous observations and it was found that their redshifts are up to z=9.4 with $\langle$ z $\rangle\approx$0.5 for SGRBs and $\langle$z$\rangle \approx$2.0 for LGRBs [18]. The energy content 51 released in a GRB is $\sim$10 erg.
In some cases of LGRBs there was observed supernova component in the lightcurve or in the spectrum of its afterglow, peaking $\sim$2 weeks after the initial trigger \cite{grb13}. LGRBs are associated with the brightest regions of galaxies and with the most massive stars \cite{grb14}. The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5]. The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 \cite{grb15}.

@@

Observations suggest that SGRBs arise from old astrophysical populations. The beaming angles for SGRBs jets seems to be from $\sim$5 to > 25 \cite{grb16}. The model that they originate in the merger of two NS has been recently confirmed by the detection of the gravitational wave (GW) signal by LIGO / Virgo collaboration 1, 2. This GW signal was accompanied with a SGRB detected by the Fermi /Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}. In case of SGRBs a kilonova/macronova can be observed. It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/grb_spectra.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

@@

In spite of great theoretical and observational successes over the last four decades, many key questions remain about the physics of GRBs. For a detailed review see \cite{grb19}. Some of these key questions are following.

Central engine: it is usually considered that as a result of the core collapse of a massive star or as a result of a merger of two compact objects there is a newborn BH created. Some models also consider that instead of a BH, a rapidly rotating NS with strong surface magnetic field (magnetar), B$\geqslant	$10$^{11}$ T, is formed. Another suggested possibility is a formation of a never observationally confirmed quark star composed of quark matter.
The particle acceleration mechanism in the relativistic shocks and the microphysics of the shocks is a major open issue in the GRB physics. 
GRB jet composition: it is still debated if the GRB outflow is baryonic or magnetic field (Poynting flux) dominated. The jet composition is tied to whether GRBs can accelerate protons to ultra-high energies and produce Ultra-High Energy Cosmic Rays (UHECRs) and high energy neutrinos. The models which expect GRBs to be sources of UHECR and high energy neutrinos invoke a baryon-dominated outflow.
Radiation mechanism: the prompt emission of GRBs is non-thermal, smoothly-joint broken-power-law called “Band” function. The emission is required to be produced by a population of particles, e.g. leptons, with a power law distribution of their energies. The main assumed mechanisms are synchrotron radiation, Synchrotron Self-Compton radiation, and Compton up-scattering of thermal photons however it is difficult to identify the correct radiation mechanism with the current available
data.
First stars (Pop III): what is the expected signature of GRBs originating in the death of the first metal-free massive stars at high redshift? It was estimated that the mass of the BH at the center of the collapsar of Pop III star is a factor of ten larger and Pop III GRBs may thus tend to have larger durations than those of ordinary Pop I and Pop II GRBs \cite{grb20}.
Classification: there are cases of GRBs which do not exactly fit in the usual short/long classification.
For example the ultra-long GRBs or short GRBs with soft extended emission. Next question is what is
the nature of the precursors in some of the GRB light curves?
Recent detection of the electromagnetic (EM) signal of the short GRB 170817A \cite{grb21} associated with a GW signal GW170817 produced by a binary neutron star (BNS) merger \cite{grb17} marks a milestone in the multi-messenger research of GRBs and means a great importance of the efforts of searching for EM counterparts to GW sources with spaceborn instruments. The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A. Approximately 1.7 prior to this GRB, LIGO-Virgo detector network observed a GW signal GW170817 at 12:41:04.4 UTC which originated from a BNS inspiral. The source was localized 9/89within a sky region of 28 deg 2 (90 \% probability), which was the most precisely localized GW signal yet. An extensive observing campaign was launched across the electromagnetic spectrum leading to the discovery of a bright optical transient in NGC 4993. Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL \cite{grb22}, Chandra X-ray Observatory \cite{grb23}, Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected \cite{grb24}.
Some models predict also EM signal from BBH coalescence, for example \cite{grb25}. More detections of EM counterpart to GW sources and kilonovae are indeed essential for better understanding of these phenomena and this proposed mission has a great potential to bring new and valuable observational data.
After the upgrades of LIGO, following the finished observing run O2, there will be O3 run scheduled to start in 2018. Further observing runs are expected after next improve of the sensitivity. Designed sensitivity is aimed to be achieved in 2021. The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s \cite{grb26}. Therefore, more GW detections are expected during the operation of this proposed mission.

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/fovvsloc.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/satellite_modules.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/scint_on_sate.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/histo_for_det.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/AtlasHalf.jpg}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/spectracsitl.png}
\caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/qe.png}
\caption{The reflectivity $\cite{esr}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/reflectivity.png}
\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

\begin{figure}
\includegraphics[width=130.0mm]{images/1channelelectronics.png}
\end{figure}

@@

\begin{itemize}
\item Scintillation yield (Number of photons produced by given keV depleted in the scintillator)
\item The energy spectra of the produced scintillation
\item The time constant of the scintillation photon creation
\item The absorbtion length of the optical photons
\item Birks constant?
\end{itemize}

@@

\includegraphics[width=150.0mm]{images/irradiation.png}

@@

\subsection{Fine tuning the optical parameters}

Most relevant parameters:
\begin{itemize}
\item absoprtion length of the scintillator material
\item reflection of the ESR (Enchanced Specular Reflector) tape the is wrapped around the scintillator 
\item scintillation yield
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics[width=130.0mm]{images/2channelsetup.png}[H!]
\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
\end{figure}

\includegraphics[width=130.0mm]{images/2channelelectronics.png}

\begin{figure}[H]
\centering
\includegraphics[width=160.0mm]{images/2channel.png}
\caption{Simulation of 100 $\gamma$s emitted from the source. The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation. Only the photons that were detected are drawn.}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
 \end{figure}

@@

\begin{figure}
\includegraphics[width=150.0mm]{images/satellite_rad.png}
\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	1100	& 	As you wish	& 	100\\
 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite}
\end{table}

\begin{table}

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
Material name & &&&&&&&&&&& \\\hline

@@

Histogram without fluorescence, turned out in LXeEMPhysics line 140-159

Histogram with flo

\begin{figure}
\centering
\includegraphics[width=140.0mm]{images/fluovsnofluo.png}
\caption{The positions of irradiation for the investigation of the response of the scintillator}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
\end{figure}

@@

@@

@@

In order to simulate how the XXX CubeSat would interact with the cosmic background and how sensitive it would be to the GRBs that it is designed to investigate a Geant4 simulation was built.

As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the particle detector of the satellite -- was implemented in Geant4. The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs that was used to read out the scintillator.

Secondly, the CAD model of the satellite was exported to Geant4. The body of the satellite was divided into 8 modules. The chemical components of these modules were included in the simulation. The scintillator was placed on the side of the satellite.

Thirdly, the effect of cosmic radiation was invastigated by obtaining the energy spectra of cosmic protons and electrons at the XXX altitude of XXX. The satellite was radiated by these particles in Geant4 from all directions to investigate how large the signal of these particles would be. This needs to be minimalized as it versenyez with the signal of gamma particles from GRBs.

Finally, the $\gamma$ absorption of the satellite was invastigated.

>>>>

The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs with the Constellation Gamma (Camelot)  CubeSats (miniaturized satellites). The Geant4 simulation described in this paper also predicts the background signal originating from solar and cosmic protons and electrons.

First the parameters of the simulation had to be fine tuned to reproduce the measured spectra in the laboratory. The simulation of the number of optical photons being deteted was sufficent to predict the signal as the electronic amplification is linear.

The build up of the satellite is quite complex, consisiting of 9 modules, each with a specific material composition. Therefore the CAD model of the satellite was imported into Geant4 in order to understand how the satellite itself would affect the measurements. The "calibrated" scintillator afterwards was placed on the side of the satellite.

Three cases were investigated. First, the model of the detector and the satellite was radiated with a parallel gamma beam that had the same parameters as GRB 9900123, the reference GRB chosen. The position of the source was rotated spherically around the satellite. In this way the absorbtion of $\gamma$s in the material of the satellite was investigated.

Secondly the cosmic background induced by the protons and electrons was simulated. The energy spectrum of electrons and protons was obatined from the SPENVIS information system. The satellite was radiated with these given energy distributions and fluxes.

@@

Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} are one of the most invesitaged and yet less understood astrophysical objects. The have been studied for more than fourty years as one of the most extreme explosive events in the Universe. Their origin is still not yet fully understood. GRBs were discovered in years 1967–73 by military satellites. The scientific community only got to know their existance in the early seventies \cite{grb5}. A GRB event is brighter than any other object in the sky during their appearance that can last from millisecond to minutes. Every day the a new GRB is observed by the satellites investigating them. The main part of the energy spectrum of these events is from the keV to the MeV ranges.

After a decade of investigation it was found that these events can be categorized into two groups by their length \cite{grb6,grb7,grb8}. The first group is called long GRBs with softer spectrum and with prompt $\gamma$-ray emission of $\geqslant$2 s. These GRBs were linked to the gravitational collapses of massive stars. These objects are associated  with type Ic core-collapse supernovae. The second group of GRBs are called short GRBs as their prompt $\gamma$-ray emission lasts $\leqslant$2 s. These objects also pocess a harder spectrum. They were linked to the merge of two very compact objects, such as neutron star - neutron star (NS-NS) and neutron star - black hole (NS-BH) mergers \cite{grb9}.

@@

One of the most accepted theories describe GRBs as collisions of highly relativistic outflow of the accelerated jetted matter \cite{grb10}. For most of the observed GRBs the prompt $\gamma$-ray emission was followed by longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11}. This is due to the propagation of a relativistic shockwave through the medium that surrounds the burst. Obsrvations proved that GRBs are at cosmological distances \cite{grb12}. The farthest GRB observed was at a distance of z=9.4. The avarge short GRBs lie at a distance of z=0.5. The long GRBs are even farther away, on avarage at z=2. The energy that is released is tremendous, about 10 erg. Long GRBs have been linked to the brightest regions of galaxies that contains the the most massive stars \cite{grb14}. %The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5]. The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 \cite{grb15}.

@@

On the contrary, short GRBs are thought to originate in old populations. The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves of such an event. This was detected by the LIGO/Virgo collaboration in 2017 \cite{gravwave}. The electromagnetic counterpart of this gravitational wave event was detected as a short GRB by the Fermi/Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}. Short GRBs emit electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/grb_spectra.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\label{fig:grb_band}
\end{figure}

@@

Despite the fact that GRBs have been studied for more than fourty years a lot of questions are still not understood about their physics\cite{grb19}. In the following the main open questions are listed:

\begin{itemize}
\item{Classification: some of the observed light curves can not be classified into short and long GRBs, such as the ultra-long GRBs.}
\item{Central engine: in most cases it is thought that a black hole is formed after the merging of neutron stars and core collapse of massive starts. Although there are models that predict the birth of a magnetar. The most exotic theories predict the birth of a quark star that has never yet been observed.}
\item{Acceleration mechanism of the jets: How particles are accelerated to a velocity of Lorentz-factor of 300 in the shock waves is not yet understood.}
\item{GRB jet composition: there are two possible driving forces behind the acceleration of jet material. The first one is magnetic field dominated and the other one is dominated by baryons. As the acceleration of particles is not yet fully understood, it is not known whether protons can be accelerated to ultra-high energies. These could produce Ultra-High Energy Cosmic Rays.} 
\item{Radiation mechanism: there are several physical processes that create the $\gamma$-ray spectrum of GRBs, that is called  the "Band" function. The following three processes are though to be the main contributors to the spectrum: synchrotron radiation, synchrotron self-compton radiation and Compton up-scattering of thermal photons.}
\item{First stars: different population of stars on avarage have different masses. Models predit that population III stars end their life with a black hole that has a mass about ten times bigger than population I and II stars. The progenitors of GRBs can be classified into populations by their redshift \cite{grb20}.}

\end{itemize}

\subsection{Search for the electromagnetic counterparts of gravitational wave events}

Multi-messenger astronomy is based on the investigation of astronomical objects with disparate "messengers". It opened a possibility gather information in different ways to understand astrophysical objects. Until 2017 the three messenger were electromagnetic radiation, cosmic rays and neutrinos. 2017 opened a new era in multi-messenger astronomy as the electromagnetic counterpart of GW signal GW170817 was detected by the LIGO/Virgo collaboration. The source of this signal was the short GRB 170817A \cite{grb21}, a binary neutron star merger \cite{grb17} marks.

The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A. Approximately 1.7 prior to this GRB, LIGO-Virgo detector network observed a GW signal GW170817 at 12:41:04.4 UTC which originated from a BNS inspiral. The source was localized 9/89within a sky region of 28 deg 2 (90 \% probability), which was the most precisely localized GW signal yet. An extensive observing campaign was launched across the electromagnetic spectrum leading to the discovery of a bright optical transient in NGC 4993. Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL \cite{grb22}, Chandra X-ray Observatory \cite{grb23}, Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected \cite{grb24}.
Some models predict also EM signal from BBH coalescence, for example \cite{grb25}. More detections of EM counterpart to GW sources and kilonovae are indeed essential for better understanding of these phenomena and this proposed mission has a great potential to bring new and valuable observational data.
After the upgrades of LIGO, following the finished observing run O2, there will be O3 run scheduled to start in 2018. Further observing runs are expected after next improve of the sensitivity. Designed sensitivity is aimed to be achieved in 2021. The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s \cite{grb26}. Therefore, more GW detections are expected during the operation of this proposed mission.

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/fovvsloc.png}
\caption{The field of view and localization accuracy of several missions}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/satellite_modules.png}
\caption{The modules of the satellite}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/scint_on_sate.png}
\caption{Side extensions including of the CAMELOT satellite (left) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right)}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/histo_for_det.png}
\label{fig:spectras_meas}
\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/AtlasHalf.jpg}
\caption{The Geant4 simulation of the whole ATLAS experiment}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/spectracsitl.png}
\caption{The emitted scintillation light spectra of three types of scintillators. In our experiment CsI(Tl) was used}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/qe.png}
\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/reflectivity.png}
\caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
\end{figure}

@@

We obtained energy spectra by using two radioisotopes (109Cd and 241Am) to evaluate the performance of our CsI scintillator + MPPC system. We placed a CsI scintillator and an MPPC in an aluminum case (2 mm thick) installed in the thermostatically controlled chamber (ESPEC LU-113). We set the operating temperature to 25C. We first tested a one-MPPC readout by using a commercial charge-sensitive preamplifier (CLEAR-PULSE 5028), a shaping amplifier (EG\&G ORTEC 571), and an ADC (AMPTEC MCA800A). We set the shaping time to 1 $\mu$s. We then tested a two-MPPC readout by using an 3 FADC Board (SHIMAFUJI Electric) originally developed for an astrophysical polarimetry mission PoGO+ [9] in order to read and sum the signals of coincident events; the shaping time for this test was set at 2.2 $\mu$s.
Figure 1 shows the setup of the experiment. We installed two lead sheets (identical in size to the scintillator) to collimate signals from the radioisotopes(3.3). We tested two CsI scintillators obtained from Amcrys with different sizes (150  75  5 mm3 and 100  75  5 mm3). Each was covered with one layer of ESR as a reflector. We used one of the latest-model MPPCs by Hamamatsu Photonics, namely, S13360-6050CS, which has an active area of 6  6 mm2 [10]. We attached an MPPC to the center of the narrower side plane of the scintillator (with an area of 75  5 mm3) for the one-MPPC readout. For the two-MPPC readout, we attached the MPPCs 18.75 mm from the edge of the plane. The breakdown voltages of the two-MPPCs are almost the same–50.82 and 50.87 V–at 25 C. We used a KEITHLEY 2400 to supply the operational voltage of 53.4 V. In analyzing of the obtained data, we evaluated four items:
the light yields of the two scintillators, the energy thresholds, the
uniformity of the light yield, and the energy resolution.

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right}
 \end{figure}

\begin{figure}
\includegraphics[width=130.0mm]{images/1channelelectronics.png}
\caption{The schematic design of the readout of the MPPC for the 1 channel configuration}
\label{fig:el1ch}
\end{figure}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|} 
 \hline
 Energy [eV] & 3.54 & 3.10 & 2.76*eV & 2.48*eV & 2.36*eV & 2.25*eV & 2.07*eV & 1.91*eV\\\hline
 Relative emittance & 0.02 & 0.1 & 0.3 & 0.6 & 0.9 & 1.0 & 0.7 & 0.4 \\\hline
 Refractive index & 1.59 & 1.57 & 1.54 & 1.54 & 1.54 & 1.54 & 1.54 & 1.54 \\\hline
 Absorption lengh [cm] & 50 & 50 & 50 & 50 & 50 & 50 & 50 & 50  \\\hline

 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite}
\end{table}

%  CsI_mt->AddConstProperty("RESOLUTIONSCALE",1.0);
%  CsI_mt->AddConstProperty("SLOWTIMECONSTANT",200.*ns);
%  CsI_mt->AddConstProperty("YIELDRATIO",1.0);

% G4double glass_RIND[lxenum]={1.49,1.49,1.49};
%  G4double glass_AbsLength[lxenum]={420.*cm,420.*cm,420.*cm};  
%  G4double reflectivity[num] = {0.995, 0.995};
%G4double photocath_EFF[num]={1.,1.}; //Enables 'detection' of photons
%  G4double photocath_ReR[num]={1.92,1.92};
%  G4double photocath_ImR[num]={1.69,1.69};

\begin{itemize}
\item Scintillation yield (Number of photons produced by given keV depleted in the scintillator): 540 1/keV
\item The time constant of the scintillation photon creation: 200 ns (exponential decay)
\end{itemize}

@@

\begin{figure}
\includegraphics[width=150.0mm]{images/irradiation.png}
\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
\end{figure}

@@

@@

\begin{figure}[h!]
\centering
\includegraphics[width=130.0mm]{images/2channelsetup.png}[H!]
\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=130.0mm]{images/2channelelectronics.png}
\caption{The schematic design of the readout electronics of the 2 channel setup}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=160.0mm]{images/2channel.png}
\caption{Simulation of 100 $\gamma$s emitted from the source. The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation. Only the photons that were detected are drawn.}
\label{fig:sim_setup}
\end{figure}

@@

\begin{figure}[h!]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
 \end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/satellite_rad.png}
\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
\end{figure}

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	1100	& 	As you wish	& 	100\\
 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
Material name & &&&&&&&&&&& \\\hline

@@

The measured spectra of the scintillation light created by $\gamma$-rays (fig. \ref{fig:spectras_meas}) has a main peak that corresponds to the 60 keV $\gamma$s from the $^{241}$Am source. There is an additional peak with an amplitude of roughly 20 \% of the main peak. The physical process that is behind this is the X-ray fluoresence. By default this process is not included in the Geant4 simulations, thus I had to turn it on. A histogram with and without x-ray fluorescence can be seen in fig. \ref{fig:fluo}

\begin{figure}[h!]
\centering
\includegraphics[width=140.0mm]{images/fluovsnofluo.png}
\caption{The obtained energy spectra from simulation with and without x-ray fluoresence being turned on. One can see that, the first peak, which can be seen in the experiments only appear when x-ray fluorescence was turned on.}
\label{fig:fluo}
\end{figure}

@@

The main aim of this thesis is to predict what signal the satellite would measure in space. In order to fine tune the parameters of the simulation experimental data was used. The light yield from different parts of the detector is different as scintillation photons have to travel a different distance and they need to be reflected back from the ESR tape that is wrapped around the detector.

\begin{figure}[h!]
\centering
\includegraphics[width=80.0mm]{images/positions.png}
\caption{The positions of irradiation for the investigation of the response of the scintillator}
\end{figure}

A lead sheet was drilled with nine holes to collimate the $\gamma$ source to certain parts of the scintillator. These measurements were carried out by Kento Torigoe at the University of Hiroshima. This configuration with a lead sheet was built up in Geant4 (fig. \ref{fig:sim_setup} and 3.6 million $\gamma$s were simulated at each position.

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.642 & 0.664 & & 70.7 & 0.743 & & 0.598 & &  \\ 
 \hline
\end{tabular}
\label{tab:exp_sim}
\caption{The position dependence of the photon yield measured at the Univeristy of Hiroshima by Kento Torigoe}
\end{center}
\end{table}

The three most relevant parameters of the setup in this case are the scintillation photon yield of the scintillator, the reflection rate of the ESR tape and the self-absorption of the scintillator. The photon yield was fixed to 540 $keV^{-1}$ taken from the data sheet of the scintillator \cite{scinti}. The self-absorption and the reflection rate was increased until the position dependence was the same as in the experiment (table. \ref{tabl:simulated}).

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
\end{figure}

@@

SPENVIS \cite{spenvis}

"SPENVIS is ESA's SPace ENVironment Information System, a WWW interface to models of the space environment and its effects; including cosmic rays, natural radiation belts, solar energetic particles, plasmas, gases, and "micro-particles"."

@@

CHange the mass of the payload!

@@

In order to simulate how the Camelot CubeSat would interact with the cosmic background and how sensitive it would be to GRBs that it is designed to investigate a Geant4 simulation was built.

As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the particle detector of the satellite -- was implemented in Geant4. The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs that was used to read out the scintillator. After the calibration, the results of the simulation was capable of predicting the signal that would be measured in space.

Secondly, the complex CAD model of the satellite --consisting of 7 modules, each with a give avarage material composition-- was exported to Geant4. The scintillator and its read out was placed on the side of the satellite.

Thirdly, the $\gamma$ absorption of the satellite was invastigated. Parallel $\gamma$-rays with a flux and energy distribution of GRB 9900123 (fig. \ref{fig:grb_band}) was simulated. 36 positions were investigated by varying the incident angle of the $\gamma$s around the major axis of the satellite.

The results show...
